An improved metric for the analysis of swarms

### 2017-09-29 paper.tex
Alignment Updates
Abstract

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
This paper examines the distance metric as a mechanism to measure the internal movement of agents and introduces a new \textit{magnitude based metric}. Both metrics are based upon the resultant internal movement of a swarm identified by analysing the changes in the inter-agent interactions. The two metrics differ in their approach to identifying the changes. The distance metric uses variations in the inter-agent spaces and the new metric uses the resultant magnitudes from an agent's \textit{inter-agent vector magnitudes} that are calculated from an agent's fields.

Both metrics allow a comparison of the effects of different swarming algorithms on a swarm's structure to idenfify the `level' of change in a swarms internal structure which is an indication of the amount of unnecessary movement an algorithm creates. The magnitude based metric also provides additional information by allowing the current `state' of a swarm to be identified i.e if it is expanding or cohesive.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{figures/FieldEffects}
\end{center}
\caption{Agent field effects\label{methods:FieldEffects}}
\end{figure}

@@

If the system is applying a weighted model then equation~\ref{eq:InterAgentMovement1} becomes:

@@

\begin{figure}%[H]
\begin{center}
\includegraphics[width=7cm]{figures/Stability5}
\end{center}
\caption{Vectors on line of separation} \label{methods:Stability5}
\end{figure}

@@

\begin{table}%[H]
\begin{center}
\begin{tabular}{| p{2.5cm} | c | p{3cm} |}
\hline
\bf Weight \bf Component & \bf Setting & \bf Description \\ \hline
Sample Rate & 100 & ms - Unit sampling interval\\  \hline
$k_c$ & 5 & weight adjuster for cohesion bias\\  \hline
$k_r$ & 15 & weight adjuster for repulsion  bias\\  \hline
$k_d$ & 0 & weight adjuster for directional bias 0 for static baseline 100 from directional\\  \hline
Repulsion Boundary & 70 & units\\  \hline
Neighbour Distance & 80 & units\\  \hline
Speed & 20 & units/s\\  \hline
\end{tabular}\caption{Swarm model parameters} \label{tab:MetricPhysics1}
\end{center}
\end{table}

@@

\begin{figure}%[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability1}
\end{center}
\caption{Internal movement cohesion (no repulsion)} \label{methods:Stability1}
\end{figure}

\begin{table}%[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
0 &	1 &	3 	 & 70.50359 &	{\color{green}352.51799} &	{\color{red}0} \\ \hline
0 &	1 &	100 & 71.78005 &	{\color{green}358.90027} &	{\color{red}0} \\ \hline
0 &	1 &	151 & 78.33995 &	{\color{green}391.69979} &	{\color{red}0} \\ \hline
0 &	2 &	99  &	72.04066 &	{\color{green}360.20334} &	{\color{red}0} \\ 
\hline
\end{tabular}\caption{Data extract ($|k_rv_r| = 0$)} \label{tab:SampleReplusion0}
\end{center}
\end{table}

@@

\begin{figure}%[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability2}
\end{center}
\caption{Internal movement repulsion} \label{methods:Stability2}
\end{figure}

\begin{table}%[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
0 & 1 & 2 & 28.32522 & {\color{green}141.62612} & {\color{red}1544.86014} \\ \hline
0 & 1 & 6 & 41.48517 & {\color{green}207.42586} & {\color{red}721.71736} \\ \hline
0 & 1 & 7 & 35.26412 & {\color{green}176.32064} & {\color{red}1034.27101} \\ \hline
0 & 1 & 8 & 43.54503 & {\color{green}217.72518} & {\color{red}637.90759} \\
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| < |k_rv_r|$)} \label{tab:SampleReplusionPositive}
\end{center}
\end{table}

@@

\begin{figure}%[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability3}
\end{center}
\caption{Internal movement cohesion and repulsion} \label{methods:Stability3}
\end{figure}

\begin{table}%[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} & {\color{red}Repulsion} 	\\ \hline
0 & 1 & 5 &	64.17214 &	{\color{green}320.86072} &	{\color{red}95.35676} \\ \hline
0 & 1 & 9 &	63.88049 &	{\color{green}319.40248} &	{\color{red}100.58590} \\ \hline
0 & 1 & 95 & 65.61522 &	{\color{green}328.07613} &	{\color{red}70.16681} \\ \hline
0 & 1 & 152 & 63.10700 & {\color{green}315.5350} & {\color{red}114.68844} \\ 
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| > |k_rv_r|$)} \label{tab:SampleCohesionPositive}
\end{center}
\end{table}

@@

\begin{figure}%[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability4}
\end{center}
\caption{Internal movement equilibrium} \label{methods:Stability4}
\end{figure}

\begin{table}%[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
7 & 76 &	91 & 55.39031 & {\color{green}276.95156} & {\color{red}276.94684} \\ \hline
24 & 75 & 6 & 55.39032 & {\color{green}276.95160} & {\color{red}276.94661} \\ \hline
32 & 72 & 38 &	55.39002603773678 & {\color{green}276.95013} & {\color{red}276.95370} \\ \hline
35 &	63 & 64 & 55.39022 &	{\color{green}276.95113} &	{\color{red}276.94887} \\
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| \approx |k_rv_r|$)} \label{tab:SampleEquilibrium}
\end{center}
\end{table}

@@

\begin{figure}%[H]
\begin{center}
\includegraphics[width=6cm]{figures/StabilityNullVector}
\end{center}
\caption{Equilibrium with null vectors} \label{methods:StabilityNullVector}
\end{figure}

@@

\begin{figure}%[H]
\begin{center}
	 \includegraphics[width=5.5cm]{figures/StabilityNullVector3}
\end{center}
\label{concave:VoidPerimeter1}
\caption{(t)}
\end{figure}

\begin{figure}
\begin{center}
	 \includegraphics[width=6cm]{figures/StabilityNullVector2}
\end{center}
\caption{(t + 1)}
\label{concave:VoidPerimeter2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineDistance1}
\end{center}
\caption{Baseline internal movement - distance\label{coord:BaselineDistance1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=9cm]{figures/BaselineMagnitude1}
\end{center}
\caption{Baseline internal movement - magnitude\label{coord:BaselineMagnitude1}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{figures/FieldEffects2}
\end{center}
\caption{Complex swarm interactions\label{additional:fieldsWork}}
\end{figure}

>>>>

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/
\usepackage{float}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
An important criteria in the application of swarm coordination algorithms is the extent to which they cause unnecessary movement. i.e. movement which occurs as a side affect of the algorithm rather than the the intended function. This paper examines the widely used distance metric as a mechanism to measure the internal movement of agents and introduces a new \textit{magnitude based metric}.

Both metrics are based upon the resultant internal movement of a swarm identified by analysing the changes in the inter-agent interactions. The two metrics differ in their approach to identifying the changes. The distance metric uses variations in the inter-agent distances and the new metric uses the resultant magnitudes from \textit{inter-agent vector magnitudes} which we claim offers a number of advantages over the distance metric.

Both metrics allow a comparison of the effects of different swarming algorithms on a swarm's structure to identify the `level' of change in a swarm's internal structure which is an indication of the amount of unnecessary movement an algorithm creates.

The magnitude based metric also identifies a swarm as expanding or cohesive.
This additional information has practical benefits for the implementation of algorithms for hetrogenious swarms.

\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/FieldEffects}
\end{center}
\caption{Agent field effects\label{methods:FieldEffects}}
\end{figure}

@@

If a weighted model is used then equation~\ref{eq:InterAgentMovement1} becomes equation~\ref{eq:InterAgentMovement2}.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=7cm]{figures/Stability5}
\end{center}
\caption{Vectors on line of separation} \label{methods:Stability5}
\end{figure}

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{| p{2.5cm} | c | p{3cm} |}
\hline
\bf Weight \bf Component & \bf Setting & \bf Description \\ \hline
Sample Rate & 100 & ms - Unit sampling interval\\  \hline
$k_c$ & 5 & weight adjuster for cohesion bias\\  \hline
$k_r$ & 15 & weight adjuster for repulsion  bias\\  \hline
$k_d$ & 0 & weight adjuster for directional bias 0 for static baseline 100 from directional\\  \hline
Repulsion Boundary & 70 & units\\  \hline
Neighbour Distance & 80 & units\\  \hline
Speed & 20 & units/s\\  \hline
\end{tabular}\caption{Swarm model parameters} \label{tab:MetricPhysics1}
\end{center}
\end{table}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability1}
\end{center}
\caption{Internal movement cohesion (no repulsion)} \label{methods:Stability1}
\end{figure}

\begin{table}[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
0 &	1 &	3 	 & 70.50359 &	{\color{green}352.51799} &	{\color{red}0} \\ \hline
0 &	1 &	100 & 71.78005 &	{\color{green}358.90027} &	{\color{red}0} \\ \hline
0 &	1 &	151 & 78.33995 &	{\color{green}391.69979} &	{\color{red}0} \\ \hline
0 &	2 &	99  &	72.04066 &	{\color{green}360.20334} &	{\color{red}0} \\ 
\hline
\end{tabular}\caption{Data extract ($|k_rv_r| = 0$)} \label{tab:SampleReplusion0}
\end{center}
\end{table}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability2}
\end{center}
\caption{Internal movement repulsion} \label{methods:Stability2}
\end{figure}

\begin{table}[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
0 & 1 & 2 & 28.32522 & {\color{green}141.62612} & {\color{red}1544.86014} \\ \hline
0 & 1 & 6 & 41.48517 & {\color{green}207.42586} & {\color{red}721.71736} \\ \hline
0 & 1 & 7 & 35.26412 & {\color{green}176.32064} & {\color{red}1034.27101} \\ \hline
0 & 1 & 8 & 43.54503 & {\color{green}217.72518} & {\color{red}637.90759} \\
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| < |k_rv_r|$)} \label{tab:SampleReplusionPositive}
\end{center}
\end{table}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability3}
\end{center}
\caption{Internal movement cohesion and repulsion} \label{methods:Stability3}
\end{figure}

\begin{table}[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} & {\color{red}Repulsion} 	\\ \hline
0 & 1 & 5 &	64.17214 &	{\color{green}320.86072} &	{\color{red}95.35676} \\ \hline
0 & 1 & 9 &	63.88049 &	{\color{green}319.40248} &	{\color{red}100.58590} \\ \hline
0 & 1 & 95 & 65.61522 &	{\color{green}328.07613} &	{\color{red}70.16681} \\ \hline
0 & 1 & 152 & 63.10700 & {\color{green}315.5350} & {\color{red}114.68844} \\ 
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| > |k_rv_r|$)} \label{tab:SampleCohesionPositive}
\end{center}
\end{table}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/Stability4}
\end{center}
\caption{Internal movement equilibrium} \label{methods:Stability4}
\end{figure}

\begin{table}[H]
\begin{center}
\begin{tabular}{| l | l | l | l | l | l |}
\hline
Log &	Id &	N.Id &	Distance &	{\color{green}Cohesion} &	{\color{red}Repulsion} 	\\ \hline
7 & 76 &	91 & 55.39031 & {\color{green}276.95156} & {\color{red}276.94684} \\ \hline
24 & 75 & 6 & 55.39032 & {\color{green}276.95160} & {\color{red}276.94661} \\ \hline
32 & 72 & 38 &	55.39002603773678 & {\color{green}276.95013} & {\color{red}276.95370} \\ \hline
35 &	63 & 64 & 55.39022 &	{\color{green}276.95113} &	{\color{red}276.94887} \\
\hline
\end{tabular}\caption{Data extract ($|k_cv_c| \approx |k_rv_r|$)} \label{tab:SampleEquilibrium}
\end{center}
\end{table}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{figures/StabilityNullVector}
\end{center}
\caption{Equilibrium with null vectors} \label{methods:StabilityNullVector}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
	 \includegraphics[width=5.5cm]{figures/StabilityNullVector3}
\end{center}
\label{concave:VoidPerimeter1}
\caption{(t)}
\end{figure}

\begin{figure}[H]
\begin{center}
	 \includegraphics[width=6cm]{figures/StabilityNullVector2}
\end{center}
\caption{(t + 1)}
\label{concave:VoidPerimeter2}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=9cm]{figures/BaselineDistance1}
\end{center}
\caption{Baseline internal movement - distance\label{coord:BaselineDistance1}}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=9cm]{figures/BaselineMagnitude1}
\end{center}
\caption{Baseline internal movement - magnitude\label{coord:BaselineMagnitude1}}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=8cm]{figures/FieldEffects2}
\end{center}
\caption{Complex swarm interactions\label{additional:fieldsWork}}
\end{figure}
